### 2009-05-25 doc/tech_doc/infosys/infosys_technical.tex
Fixing sparsity value typo
Adding example ISIS configuration to the technical documentation as an appendix.

Every node has always exactly n = $\lceil \log_s{N} \rceil$ neighbors where the $N$ is the number of ISIS nodes registered into the network. The node has as many neighbors as the ISIS nodes with PeerID $s^0$-th, $s^1$-th ... $s^{n-1}$-th greater than its own. (For example: There are 19 nodes in this network with sparsity=9. Then the first node has the following neighbors: the 2nd, 3rd, 5th, 9th, and 17th node as seen in figure \ref{fig:p2p_neighbors_2}.)

@@

>>>>

Every node has always exactly n = $\lceil \log_s{N} \rceil$ neighbors where the $N$ is the number of ISIS nodes registered into the network. The node has as many neighbors as the ISIS nodes with PeerID $s^0$-th, $s^1$-th ... $s^{n-1}$-th greater than its own. (For example: There are 19 nodes in this network with sparsity=2. Then the first node has the following neighbors: the 2nd, 3rd, 5th, 9th, and 17th node as seen in figure \ref{fig:p2p_neighbors_2}.)

@@

\section{Example ISIS service configuration}
\label{annex:example_isis_configuration}
\begin{verbatim}
<ArcConfig
  xmlns="http://www.nordugrid.org/schemas/ArcConfig/2007"
  xmlns:tcp="http://www.nordugrid.org/schemas/ArcMCCTCP/2007"
  xmlns:isis="http://www.nordugrid.org/schemas/isis/2008/08"
  xmlns:infosys="http://www.nordugrid.org/schemas/InfoRegisterConfig/2008"
>
  <!-- Various server settings -->
  <infosys:InfoRegistrar id="NorduGridInfosys">
    <!-- Contact and behavior details of the InfoRegsitrar element-->
    <infosys:URL><!-- Available endpoint URL of an ISIS representing the cloud --></infosys:URL>
    <infosys:Retry>4</infosys:Retry>
  </infosys:InfoRegistrar>

  <Plugins><Name>isis</Name></Plugins>

  <Chain>

    <!-- Chain configuration goes here! -->
    <Plexer name="plexer.service" id="plexer">
      <next id="isis1">^/isis1$</next>
    </Plexer>

    <Service name="isis" id="isis1">
        <isis:DBPath>
            <!-- File location where the database is locally stored -->
        </isis:DBPath>
        <isis:endpoint>
            <!-- The URL where the service can be accessed from outside -->
        </isis:endpoint>
        <isis:InfoProviderISIS>
            <isis:URL>
                <!-- The URL of one or more ISIS where the other ISIS's can be queried. -->
            </isis:URL>
        </isis:InfoProviderISIS>
        <infosys:InfoRegister>
            <infosys:Period>
                <!-- How often should the service be registered. 
                For example: PT75S for 75 seconds -->
            </infosys:Period>
            <infosys:Endpoint>
                <!-- The URL where the service can be accessed from outside -->
            <infosys:Endpoint>
            <infosys:Expiration>
                <!-- The lifetime of the RegEntry provided by the service about itself.
                For example: PT5H for 5 hours -->
            </infosys:Expiration>
            <!-- If there is no specific Registrar defined then every InfoRegistrar
             will be use used during the registration. The period of the repeating 
             registration will be the value given here in every ISIS cloud. -->
        </infosys:InfoRegister>
    </Service>
  </Chain>
</ArcConfig>

\end{verbatim}
% section example_ISIS_configuration (end)
